---
output: github_document
bibliography: README-references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# eventstream

  [![Travis build status](https://travis-ci.org/sevvandi/eventstream.svg?branch=master)](https://travis-ci.org/sevvandi/eventstream)

The goal of *eventstream* is to extract and classify events in data streams. For details see [@eventstream].  The R scripts used in the paper are at  https://github.com/sevvandi/eventstream_paper .

This package is still under development and this repository contains a development version of the R package *eventstream*.

## Installation

You can install *eventstream* from github with:


``` r
#install.packages("devtools")
devtools::install_github("sevvandi/eventstream")
```

## Generate data

This is an example of a data stream you can generate with *eventstream*. 
The extracted events are plotted for the first 2 windows using a window size of 200 and a step size of 50. 

```{r example}
library("eventstream")
library("AtmRay")
library("ggplot2")
str <- gen_stream(3, sd=1)
zz <- str$data
dat <- as.data.frame(t(zz))
dat.x <- 1:dim(dat)[2]
dat.y <- 1:dim(dat)[1]
mesh.xy <- AtmRay::meshgrid(dat.x,dat.y)
xyz.dat <- cbind(as.vector(mesh.xy$x), as.vector(mesh.xy$y), as.vector(as.matrix(dat)) )
xyz.dat <- as.data.frame(xyz.dat)
colnames(xyz.dat) <- c("Time", "Location", "Value")
ggplot(xyz.dat, aes(Time, Location)) + geom_raster(aes(fill=Value)) +   scale_fill_gradientn(colours=topo.colors(12)) + theme_bw()

zz2 <- zz[1:250,]
ftrs <- extract_event_ftrs(zz2,win_size=200, step_size = 50, vis=TRUE)
```



## References